Standardization of ceramic shape: A case study of Iron Age pottery from northeastern Taiwan

### 2020-09-13 analysis/paper/paper.Rmd
update inline code for stats

pval_all <- signif(unname(sum_man_all_df[,'Pr(>F)'][1]), 4)
```

@@

Petrographic analysis for 34 thin sections presents a high percentage of inclusions (15-50%), including argillite (15-40%), metasandstone (1-10%), sandstone fragments (1-6%), quartz (1-5%), and trace amounts of feldspar and slate. Particle sizes range from 500 to 1300 microns. In general, the vessel fabric presents a mixture of fine, rounded argillite with a small amount of rounded metasandstone and rounded sub-angular monocrystalline quartz. This composition is consistent with the mineralogical composition of local raw materials found in the Yilan Plain [@Chen2016]. There are no significant changes in the inclusions over time, indicating continuity in pottery fabric composition across the three periods (p = $`r pval_all`$) [@WangandMarwick2020].

>>>>

pillai <- signif(unname(sum_man_all_df[,"Pillai's trace"][1]), 4)
F_value <- signif(unname(sum_man_all_df[,"Approximate F value"][1]), 4)
df <- signif(unname(sum_man_all_df[,"degrees of freedom"][1]), 3)
pval_all <- signif(unname(sum_man_all_df[,'Pr(>F)'][1]), 3)
```

@@

Petrographic analysis for 34 thin sections presents a high percentage of inclusions (15-50%), including argillite (15-40%), metasandstone (1-10%), sandstone fragments (1-6%), quartz (1-5%), and trace amounts of feldspar and slate. Particle sizes range from 500 to 1300 microns. In general, the vessel fabric presents a mixture of fine, rounded argillite with a small amount of rounded metasandstone and rounded sub-angular monocrystalline quartz. This composition is consistent with the mineralogical composition of local raw materials found in the Yilan Plain [@Chen2016]. There are no significant changes in the inclusions over time, indicating continuity in pottery fabric composition across the three periods (Pillai's Trace = $`r pillai`$, F = $`r F_value`$, df = $`r df`$, p = $`r pval_all`$) [@WangandMarwick2020].
